{\helveticaitalic{Supplementary Material}}

### 2022-07-17 tex/sections/discussion.tex
Add small edits
remove line labels

\section{Discussion}
% PROBLEM SUMMARY
Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming \citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}.
In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
\linelabel{line:principle}
Modelling can shed light on the underlying mathematical principles that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.

@@

% LIMITATION: SPIKE MAP
Our simulations of the network showed that $n:n$ solutions lose robustness as their period is increased.
That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength.
We were able to replicate this finding by numerically finding the respective left and right borders of stable $n:n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
\linelabel{line:disc-pincA}
We have also noted the resemblance of our bifurcation diagram to one where such $n:n$ branches are created via the bifurcation scenario of type period-increment with co-existent attractors, first described for scalar linear maps with a discontinuity \citep{avrutin2012,avrutin2011}.
It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} result from a ``reinjection'' mechanism \cite{perez1985}.
Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity.
The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods.
In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment dynamics.
It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
\linelabel{line:disc-pincB}
In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.

@@

% BIOLOGICAL IMPORTANCE OF DEPRESSION
% TODO: Perhaps mention learning after all?
We have shown that when the strength of the maximum synaptic conductance is varied, synaptic depression of inhibition can enable our two-cell network to produce burst solutions of different periods.
This result is in line with the idea that one role of synaptic depression in the nervous system may be to allow a finite size neuronal network to participate in different tasks by producing a large number of rhythms~\citep{bose2011, jalil2004, li2007}.
To change from one rhythm to another would only require a reconfiguration of the network through changes in synaptic coupling strength.
Thus short-term synaptic depression of inhibition may provide means for a network to adapt to environmental challenges without changing its topology, that is without the introduction or removal of neurons.

>>>>

\section{Discussion}
% PROBLEM SUMMARY
Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming \citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}.
In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
Modelling can shed light on the underlying mathematical principles that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.

@@

% LIMITATION: SPIKE MAP
Our simulations of the network showed that $n:n$ solutions lose robustness as their period is increased.
That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength.
We were able to replicate this finding by numerically finding the respective left and right borders of stable $n:n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
We have also noted the resemblance of our bifurcation diagram to one where such $n:n$ branches are created via the bifurcation scenario of type period-increment with co-existent attractors, first described for scalar linear maps with a discontinuity \citep{avrutin2012,avrutin2011}.
It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} result from a ``reinjection'' mechanism \cite{perez1985}.
Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity.
The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods.
In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment dynamics.
It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.

@@

% BIOLOGICAL IMPORTANCE OF DEPRESSION
We have shown that when the strength of the maximum synaptic conductance is varied, synaptic depression of inhibition can enable our two-cell network to produce burst solutions of different periods.
This result is in line with the idea that one role of synaptic depression in the nervous system may be to allow a finite size neuronal network to participate in different tasks by producing a large number of rhythms~\citep{bose2011, jalil2004, li2007}.
To change from one rhythm to another would only require a reconfiguration of the network through changes in synaptic coupling strength.
Thus short-term synaptic depression of inhibition may provide means for a network to adapt to environmental challenges without changing its topology, that is without the introduction or removal of neurons.

### 2022-07-17 tex/sections/introduction.tex
remove line labels

\begin{abstract}
  \section{}
  Short-term synaptic plasticity is found in many areas of the central nervous system.
  In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
  To better understand burst generation in these central pattern generators, we study a minimal network of two neurons coupled through depressing synapses.
  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n:n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
  Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
  This map tracks the state of synaptic depression from one burst to the next and captures the complex bursting dynamics of the network.
  Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
  \linelabel{line:abstract}
  We derive conditions that predict the bifurcations between $n:n$ and $(n+1):(n+1)$ solutions, producing a full bifurcation diagram of the burst cycle period.
  Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.

@@

% Brown
\linelabel{line:A}
~\citet{brown1911} pioneered the idea that synaptic depression acts as a burst termination
mechanism in CPGs composed of reciprocally inhibitory neurons and involved in rhythm generation of locomotion.
When one side is firing during a burst the other, antagonistic side, is prevented from
firing by synaptic inhibition.
However, the weakening of inhibition as a result of synaptic depression eventually releases the antagonistic side so that it starts firing, terminating the burst on the side that had originally been firing.
This rhythmogenesis hypothesis has been considered one of a handful of standard mechanisms for generating locomotion rhythms in vertebrates~\citep{reiss1962,perkel1974,friesen1994}.
It has been proposed as an explanation of the antiphase burst rhythm in struggling in \textit{Xenopus} tadpoles~\citep{li2007}.

~\citet{bose2011} investigated burst generation in a generic half-centre CPG that consists
of two identical, tonically active Morris-Lecar~\citep{morris1981} neurons coupled through
inhibitory depressing synapses.
Numerical simulations showed that when the reciprocal synaptic conductance between the two neurons is varied, the network produces symmetric $n:n$ anti-phase bursts, with stronger synaptic coupling leading to longer bursts.
They used methods from geometric singular perturbation theory to separate the timescales of the fast membrane, and the slow synaptic dynamics of the network to derive one-dimensional conditions necessary for the existence of stable $n:n$ solutions (for $n\leq 2$).
According to these conditions the type of firing pattern largely depends on the slow
depression dynamics of the synapses between the two neurons, and can therefore be
predicted by knowing the strengths of the synaptic conductances of the two synapses.
\linelabel{line:B}
Thus, the scalar conditions derived in \citet{bose2011} provide a method to numerically
identify the type of stable $n:n$ pattern for any given value of the coupling strength and $n\leq 2$.
However, they do not predict the exact period of such solutions.
Furthermore, while they provide good arguments for the validity of their reduction assumptions and the resulting scalar conditions, they do not verify them numerically.

>>>>

\begin{abstract}
  \section{}
  Short-term synaptic plasticity is found in many areas of the central nervous system.
  In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
  To better understand burst generation in these central pattern generators, we study a minimal network of two neurons coupled through depressing synapses.
  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n:n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
  Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
  This map tracks the state of synaptic depression from one burst to the next and captures the complex bursting dynamics of the network.
  Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
  We derive conditions that predict the bifurcations between $n:n$ and $(n+1):(n+1)$ solutions, producing a full bifurcation diagram of the burst cycle period.
  Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.

@@

% Brown
~\citet{brown1911} pioneered the idea that synaptic depression acts as a burst termination
mechanism in CPGs composed of reciprocally inhibitory neurons and involved in rhythm generation of locomotion.
When one side is firing during a burst the other, antagonistic side, is prevented from
firing by synaptic inhibition.
However, the weakening of inhibition as a result of synaptic depression eventually releases the antagonistic side so that it starts firing, terminating the burst on the side that had originally been firing.
This rhythmogenesis hypothesis has been considered one of a handful of standard mechanisms for generating locomotion rhythms in vertebrates~\citep{reiss1962,perkel1974,friesen1994}.
It has been proposed as an explanation of the antiphase burst rhythm in struggling in \textit{Xenopus} tadpoles~\citep{li2007}.

~\citet{bose2011} investigated burst generation in a generic half-centre CPG that consists
of two identical, tonically active Morris-Lecar~\citep{morris1981} neurons coupled through
inhibitory depressing synapses.
Numerical simulations showed that when the reciprocal synaptic conductance between the two neurons is varied, the network produces symmetric $n:n$ anti-phase bursts, with stronger synaptic coupling leading to longer bursts.
They used methods from geometric singular perturbation theory to separate the timescales of the fast membrane, and the slow synaptic dynamics of the network to derive one-dimensional conditions necessary for the existence of stable $n:n$ solutions (for $n\leq 2$).
According to these conditions the type of firing pattern largely depends on the slow
depression dynamics of the synapses between the two neurons, and can therefore be
predicted by knowing the strengths of the synaptic conductances of the two synapses.
Thus, the scalar conditions derived in \citet{bose2011} provide a method to numerically
identify the type of stable $n:n$ pattern for any given value of the coupling strength and $n\leq 2$.
However, they do not predict the exact period of such solutions.
Furthermore, while they provide good arguments for the validity of their reduction assumptions and the resulting scalar conditions, they do not verify them numerically.
